Dialogue act classification is a laughing matter

### 2021-07-25 reports/SemDial2021/semdial.tex
blob for experiment 2
images
test Overleaf
Updates from Overleaf

%
% File acl2021.tex
%
%% Based on the style files for EMNLP 2020, which were
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

@@

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

\usepackage{enumitem}
\newlist{lingex}{enumerate}{3} % easy numbering of examples
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}
\usepackage{adjustbox}

@@

\title{Instructions for ACL-IJCNLP 2021 Proceedings}

@@

\begin{document}
\maketitle
\begin{abstract}
What we do: i) corpus study of laughter associated with dialogue acts and ii) testing the importance of laughter for DAR
\end{abstract}

@@

\section{Corpus study}
\label{sec:corpus}

In this section we analyse dialogue acts according to their co-location with
laughter and provide some qualitative insights from the
statistics. The distribution of laughs in different dialogue acts has
a rather uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
most distinct outlier is ``Nonverbal'' dialogue act which is
misleading with respect to laughter, because utterances only
containing a single laughter token fall into this category, however
they can serve, for example, to acknowledge a statement or to deflect
a question \citep{mazzocconi2019phd}.

\begin{figure}
  \includesvg[width=\linewidth]{img/box-swda}
  \caption{Box plot for proportions of dialogue act which contain laughs.}
  \label{fig:box-swda}
\end{figure}

Let us introduce our comparison schema for the other two outliers,
Downplayer and Apology, comparing them with the most common dialogue
act in SWDA---Statement-Non-Opinion.  We take into consideration five
laughter-related dimensions of an utterance, and create 5-dimensional
representations of dialogue acts according to them. Each dimension's
value equals to the proportion of utterances of a given type which
contain laughter.
\begin{itemize}
\item[$\uparrow$] current utterance;
\item[$\nwarrow$] previous utterance by the same speaker;
\item[$\swarrow$] previous utterance by the other speaker;
\item[$\nearrow$] next utterance by the same speaker;
\item[$\searrow$] next utterance by the other speaker.
\end{itemize}

\begin{figure}
  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
  \caption{Comparison of the most common dialogue act in
    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
    of utterances which contain laughter are shown in association with
    each dialogue act. }
  \label{fig:orbit}
\end{figure}

% 1. overview: rather uniform distribution with few outliers
% 2. let's look at outliers
% 3. consider 5 dimensions of relations

For instance, 
\begin{lingex}
\item
  \adjustbox{valign=t}{
    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
    A: & I am so sorry to keep you on hold. & Apology \\
    B: & <Laughter> No problem. & Downplayer \\
    A: & Are you at work? & YN-Quest. \\
  \end{tabulary}}
\end{lingex}

\section{Laughter’s role in dialogue act recognition}
\label{sec:dar}

@@

\subsection{Data}\label{sec:data}
We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.

@@

\begin{table}[]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
Dyadic                     & Multi-party                             \\
Casual conversation        & Mock business meeting                   \\
Telephone                  & In-person \& video                      \\ \midrule
English                    & English                                 \\ 
Native speakers            & Native \& non-native speakers           \\ 
early '90s                 & 2000s                                   \\ \midrule
2200 conversations         & 171 meetings                            \\
  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
400k utterances             & 118k utterances                         \\
3M tokens                  & 1.2M tokens                             \\ \bottomrule
\end{tabular}
  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
  \label{table:corpora}
\end{table}

\paragraph{Preprocessing}
% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

We make an effort to normalize transcription conventions across SWDA and AMI.
We remove disfluency annotations and slashes from the end of utterances in SWDA.
In both corpora, acronyms are tokenized as individual letters. 
All utterances are lower-cased.

Utterances are tokenized using with a word piece tokenizer \citep{Wu2016} with a vocabulary of 30,000.
We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.

\subsection{Pre-training corpora}
We also experiment with three unlabeled dialogue corpora (Table~\ref{tab:pretraining-corpora}), which we use to provide further pre-training for the BERT encoder.

The first two corpora are constructed from the same source as the dialogue act corpora.
We use the SWDA portion of the un-labeled Switchboard corpus (SWBD) and the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
In both cases, we exclude dialogues that are reserved for DAR testing.

We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
We used a manually constructed list of words frequenty used to refer to laughter in subtitles and replaced every occurance of one of these words with the special laughter token. 
Then, we collected every English-language subtitle file in which at least 1\% of the utterances contained laughter (about 11\% of the total).
Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.

The pre-training corpora were prepared for the combined maksed language modeling and next sentence (utterance) prediction task, as described dy \citet{devlinBERTPretrainingDeep2018}.
For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data. Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}

\begin{table}[ht]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
       & tokens & \% laughs & epochs\\ \midrule
AMI           & 1M     & 1.3             & 10     \\
SWBD          & 1.5M   & 0.5             & 10     \\
OpenSubtitles & 350M   & 0.3             & 1      \\ \bottomrule
\end{tabular}
\caption{Pre-training corpora, showing laughter representation as a percentage of total tokens and number of pre-training epochs generated.}\label{tab:pretraining-corpora}
\end{table}

\paragraph{}
Let us turn now to describing the neural network architectures that we used.

\subsection{The model}
\label{sec:model}
To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN. It can be explained by the absence of longer distance dependencies on this level of our model.} 
The RNN takes the encoded utterance as input at each time step,
and its hidden state is passed to a simple linear classification layer over dialogue act tags.
Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.

@@

As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.

@@

\section{Laughter as a non-verbal dialogue act}
\label{sec:laughter-as-non}

\section{Discussion}
On the question of laughter impact, this study found that laughter is more helpful in SWDA corpus than in AMI-DA.
Due to the nature of interactions over the phone, SWDA dialogue participants can not rely on visual signals, such as gestures and facial expressions.
Our results support the hypothesis that in SWDA, vocalizations such as laughter are more pronounced and therefore more helpful in disambiguating dialogue acts.

>>>>

% File acl2021.tex
%
%% Based on the style files for EMNLP 2020, which were
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

@@

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{todonotes}

@@

\usepackage[inline,shortlabels]{enumitem}
\newlist{lingex}{enumerate}{3} % easy numbering of examples
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount,font=\small}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}
\usepackage{adjustbox}

@@

\title{Dialogue act classification is a laughing matter}

@@

\begin{document}
\maketitle
\begin{abstract}
  In this paper we explore the role of laughter in attributing
  communicative intents to utterances, i.e.\ detecting the dialogue act
  performed by them. We conduct a corpus study in adult
  phone conversations showing how different dialogue acts are
  characterised by specific laughter patterns, both from the speaker
  and from the partner. Furthermore, we show that laughs can
  positively impact the performance of Transformer-based models in a
  dialogue act recognition task.  Our results highlight the importance
  of laughter for meaning construction and disambiguation in
  interaction.
  % In this paper we explore the role of laughter in interpreting the
  % meaning of an utterance, more specifically, a dialogue act performed
  % by it. We illustrate the role of laughter in pragmatic
  % disambiguation in a corpus study, and highlight the interplay
  % between non-verbal behaviours and dialogue acts performed by
  % utterances. Furthermore, we show that laughs can positively impact the
  % performance of Transformer-based models in a dialogue act recognition
  % task.
\end{abstract}

@@

Laughter is ubiquitous in our everyday interactions.  In the
Switchboard Dialogue Act Corpus \citep[SWDA,][]{jurafsky1997switchboard} (US
English, phone conversations where two participants that
are not familiar with each other discuss a potentially controversial
subject, such as gun control or the school system) non-verbally vocalised
dialogue acts (whole utterances that are marked as non-verbal, 66\% of
which contain laughter) constitute 1.7\% of all dialogue acts.
Laughter tokens\footnote{Switchboard Dialogue Act Corpus does not include speech-laughs.} make up 0.5\% of all the tokens that occur in the
corpus.

Laughter relates to the discourse structure of dialogue
and can refer to a \emph{laughable}, which can be a perceived event or an
entity in the discourse.
Laughter can precede, follow or overlap the laughable, with the time
alignment between the laughter and laughable dependent on who produces
the laughable, the form of the laughter, and the pragmatic function performed \citep{tian2016we}. 
%Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm
% \citep{tepperman2006yeah}.% ??
% VM (removed as too vague!): Some studies have already pointed out the role of laughter to disambiguate between literal or not literal interpretations of utterances.

\citet{bryant2016laughter} shows how listeners are influenced towards a non-literal interpretation of sentences when accompanied by laughter. Similarly, \citet{tepperman2006yeah} shows that laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm. % \todo{I don't know if that's ok... and I don't know if you preferred this bit here or later in the laughter background...!
% }
% VM: it is good!

Nevertheless there is a dearth of research exploring the use of
laughter in relation to different dialogue acts in detail, and
therefore little is known about the role that laughter may have in
facilitating the detection of communicative intentions.
% for Vlad! just to let you know! I noticed the "CAN" relate to a laughable ^^
% VM: what do you mean?

In this paper we investigate the disambiguation potential of laughter
for interpreting the meaning of an utterance, with the central point
being the dialogue act performed by it. To do so, we employ a
Transformer-based model and look into laughter as a potentially useful
feature for the task of \emph{dialogue act recognition} (DAR). Laughs are not
present in a large-scale pre-trained models, such as BERT \citep{Devlin2019a}, but their
representations can be learned while training for a dialogue-specific
task (DAR in our case). We further explore whether such representations
can be additionally learned, in an unsupervised fashion, from
dialogue-like data, such as a movie subtitles corpus, and if it
further improves the performance of our model. 
% Vlad check if it is right what I have written!! XD XD
% VM: perfect

The paper is organised as follows. We start with some brief background
in Section~\ref{sec:background}. In Section~\ref{sec:corpus} we
observe how dialogue acts can be classified with respect to their
collocations with laughs and discuss the patterns observed in relation
to the pragmatic functions that laughter can perform in dialogue. In
Section~\ref{sec:dar} we report our experimental results for the DAR
task depending on whether the model includes laughter. We further
investigate whether non-verbal dialogue acts can be classified as more
specific dialogue acts by our model.  We conclude with a discussion and
outlining the directions for further work in
Section~\ref{sec:discussion}.

\section{Background}
\label{sec:background}

\subsection{Laughter}
\label{sec:laughter}
%Laughter production in conversation is not exclusively related to humour. But, perhaps unsurprisingly, the study of laughter has often been linked to the study of humour and the two terms are frequently used interchangeably. However, 
% Laughter does not occur only in
% response to humour or in order to frame it. Many studies,
% particularly in conversation analysis, have shown the role of laughter in
% managing conversations at several levels: dynamics (turn-taking and
% topic-change), lexical (signalling problems of lexical retrieval or
% imprecision in the lexical choice), pragmatic (marking irony,
% disambiguating meaning, managing self-correction) and social
% (smoothing and softening difficult situations or showing
% (dis)affiliation)
% \citep{glenn2003laughter,jefferson1984organization,mazzocconi2019phd,petitjean2015laughing}.
Laughter does not occur only in
response to humour or in order to frame it. It is crucial in managing conversations in terms of dynamics (turn-taking and
topic-change), at the lexical level (signalling problems of lexical retrieval or
imprecision in the lexical choice), but also at a pragmatic (marking irony,
disambiguating meaning, managing self-correction) and social level (smoothing and softening difficult situations or showing
(dis)affiliation)
\citep{glenn2003laughter,jefferson1984organization,mazzocconi2019phd,petitjean2015laughing}.

Moreover \citet{romaniuk2009clinton} and \citet{ginzburg2020laughter}
discuss how laughter can answer or decline to answer a question, and
\citet{mazzocconi2018laughter} discusses how even isolated laughter
can be the object of clarification requests, signalling the need for
interlocutors to clarify its meaning (e.g., in terms of what the
``laughable'' is) in order to continue the conversation.

% \textcolor{blue}{<-- this is really badly written!}
%\todo{^^ I think I'll rephrase it later!! XD I've copied and pasted these sentences in way to many places already!!! XD XD XD }

%\todo{Ah! I see now the comment! Yes! I was just about to ask you if you would agree if I say a bit about the role of laughter for expliciting/disambiguating intentions! I mean... there is not much specifically speaking explicitely about laughter and dialogue acts but quite a bit I can say about the role laughter can have to disambiguate communicative intentions! }

% Chiara: is there something more related to DAs?..

\subsection{Dialogue act recognition}
\label{sec:dial-act-recogn}

The concept of a dialogue act (DA) is based on that of the speech act
\citep{austin1975things}. %CH 2009??? Not 1975? 
Breaking with classical semantic
theory, Speech Act Theory considers not only the propositional content
of an utterance but also the actions, such as \emph{promising} or
\emph{apologising}, it carries out.  Dialogue acts extend the concept
of the speech act, with a focus on the interactional nature of most
speech.  DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an
influential DA tagging scheme where DAs are
defined in part by whether they have a \emph{forward-looking} function
(expecting a response) or \emph{backward-looking} function (in
response to a previous utterance).

Dialogue act recognition (DAR) is the task of labelling utterances with
the dialogue act they perform, given a set of dialogue act tags.  As
with other sequence labelling tasks in NLP, some notion of context is
helpful in DAR.  One of the first performant machine learning models
for DAR was a Hidden Markov Model that used various lexical and
prosodic features as input \citep{stolckeDialogueActModeling2000}.

Recent state-of-the-art approaches to dialogue act recognition
have used a hierarchical approach, using large pre-trained language models like BERT to represent utterances, and adding some representation of discourse context at the dialogue level \citep[e.g.,][]{Ribeiro2019,mehriPretrainingMethodsDialog2019}.
However \citet{darbert} observe that without fine-tuning,
standard BERT representations perform very poorly on dialogue,
even when paired with a discourse model,
suggesting that certain utterance-internal features missing
from BERT's textual pre-training data (such as laughter) 
may have an adverse effect on dialogue act recognition.

% Bill: what’s the state-of-the-art? + refer to our IWCS paper

\section{Laughs in the Switchboard Dialogue Act Corpus}
\label{sec:corpus}

In this section we analyse dialogue acts in the Switchboard Dialogue Act
Corpus according to their collocation with laughter and provide some
qualitative insights based on the statistics.

SWDA is tagged with a set of 220 dialogue act tags which, following
\citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we
cluster into a smaller set of 42 tags.

The distribution of laughs in different dialogue acts has a rather
uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
most distinct outlier is the \emph{Non-verbal} dialogue act which is
misleading with respect to laughter, because utterances only
containing a single laughter token fall into this category. However
isolated laughs can serve, for example, to acknowledge a statement, to
deflect a question, or to show appreciation
\citep{mazzocconi2019phd}. We will further conjecture on this class of
DAs in Sec.~\ref{sec:laughter-as-non}.
%is it to much if I put making a statement? too much commintment to the propositional content thingy right?! XD

\subsection{Method}
\label{sec:method}

\begin{figure}
    \fontsize{8}{10}\selectfont
  \includesvg[width=\linewidth]{img/box-swda}
  \caption{Box plots for proportions of dialogue acts which contain laughs in SWDA. On the left: proportion of DAs containing laughter, on the right: proportion of DAs having laughter in one of the adjacent utterances.}%CH: Is it justified to combine preceding and following laughters in the same plot given the differences highlighted later?
  \label{fig:box-swda}
\end{figure}

Let us illustrate our comparison schema using the other two outliers,
\emph{Downplayer} (make up 0.05\% of all utterances) and \emph{Apology} (0.04\%), comparing them with the most common dialogue
act in SWDA---\emph{Statement-Non-Opinion} (33.27\%).  We take into consideration five
laughter-related dimensions of an utterance, and create 5-dimensional
(pentagonal) representations of DAs according to them. Each
dimension's value is equal to the proportion of utterances of a given
type which contain laughter:
\begin{itemize}
\item[$\uparrow$] current utterance;
\item[$\nwarrow$] immediately preceding utterance by the same speaker;
\item[$\nearrow$] immediately following utterance by the same speaker;
\item[$\swarrow$] immediately preceding utterance by the other speaker;
\item[$\searrow$] immediately following utterance by the other speaker.
\end{itemize}

\begin{figure}
  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
  \caption{Comparison between the pentagonal representations of laughter collocations of dialogue acts.}
  \label{fig:orbit}
\end{figure}

For instance, \ref{ex:apology-downplayer} is an illustrative example
of the phenomenon shown in Figure \ref{fig:orbit}.

\begin{lingex}%CH What are # ?
\item\label{ex:apology-downplayer}\footnote{Overlapping material is marked wish hash signs.}
  \small
  \adjustbox{valign=t}{
    % \setlength\tabcolsep{1.5pt}
    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
      A: & I'm sorry to keep you waiting \#<laughter>.\# & Apology \\
      B: & \#Okay\# <laughter>. / & Downplayer \\
      A: & Uh, I was calling from work  & Statement (n/o) \\
\end{tabulary}}
\end{lingex}

We show the representations of all dialogue acts on
Figure~\ref{fig:da-orbits}. We believe that such a depiction helps
the reader form impressions about similarities  between
DAs based on their laughter collocations and notice the ones
that stand out in some respects.

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/multiorbit.pdf}
  \caption{Pentagonal representation of dialogue acts: proportions of utterances which include laughter. Dimensions:
$\uparrow$ current utterance;
$\nwarrow$ immediately preceding utterance by the same speaker;
$\nearrow$ immediately following utterance by the same speaker;
$\swarrow$ immediately preceding utterance by the other speaker;
$\searrow$ immediately following utterance by the other speaker.
DAs are ordered by their frequency in SWDA (left-to-right, then top-to-bottom).
    \label{fig:da-orbits}}
\vspace*{-0.5cm}
\end{figure*}

To further assess the similarity between dialogue acts based on their
collocations with laughs we factorise their pentagonal representations
into 2D space using singular value decomposition (SVD). We can see
that dialogue acts form some distinct clusters.
% TODO: CH's note
The resulting plot is
shown in Figure~\ref{fig:da-svd} in Appendix~\ref{sec:app:da-svd}. Let
us now proceed with some qualitative observations.

\subsection{Observations}
\label{sec:observations}
\paragraph{Laughter and modification or enrichment of the current DA}
We observe a higher proportion of laughter accompanying the current
dialogue act ($\uparrow$) when the laughter is aimed at modifying
the current dialogue act with some degree of urgency in order to
smooth or soften it (\emph{Action-directive}, \emph{Reject},
\emph{Dispreferred answer}, \emph{Apology}), to contribute to its
enrichment stressing the positive disposition towards the partner
(\emph{Appreciation}, \emph{Downplayer}, \emph{Thanking}), or to cue
for the need to consider a less probable meaning, therefore helping
in non-literal meaning interpretation (\emph{Rhetorical question}).

While \emph{Apology} and \emph{Downplayer} have rather distinct and peculiar
patterns (Fig.~\ref{fig:da-svd}) discussed in more detail below, we
observe \emph{Dispreferred answers}, \emph{Action directives},
\emph{Offers/Options/Commits} and \emph{Thanking} to constitute a
close cluster when considering the decomposed values of the pentagonal
used for DA representation.%CH ??? I don't understand this sentence!

\paragraph{Laughter for benevolence induction and laughter as a response}
The patterns observed in relation to the preceding and following
turns reflect the multitude of functions that
laughter can perform in interaction, stressing the fact that it can be
used both to induce or invite a determinate response (dialogue act) from
the partner (\emph{Downplayer}, \emph{Agree/Accept}, \emph{Appreciation}, \emph{Acknowledge})
as well as being a possible answer to specific dialogue acts
(e.g. \emph{Apology}, \emph{Offers/Options/Commits}, \emph{Summarise/Reformulate},
\emph{Tag-question}).

A peculiar case is than the one of \emph{Self-talk}, often followed by
laughter by the same speaker. In this case the laughter may be
produced to signal the incongruity of the action (in dialogue we
normally speak to others, not to ourselves), while at the same time
function to smooth the situation, for instance, when having issues of
lexical retrieval, as in \ref{ex:selftalk}, or some degree of
embarrassment from the speaker, when questioning whether a
contribution is appropriate or not, as in
\ref{ex:appropriate}.

% A[\%]: {F Oh, } what can, - /
% A[t1]: what is his name <lipsmack>.  /
% A[ba]: {F Oh, } durn <laughter>,  /

\begin{lingex}
\item\label{ex:selftalk}
  \small
  \adjustbox{valign=t}{
    % \setlength\tabcolsep{1.5pt}
    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
      A: & Have, uh, really, - &  \\
      A: & what's the word I'm looking for, & Self-talk \\
      A: & I'm just totally drawing a blank <laughter>. & Statement (n/o) \\

\end{tabulary}}

\item\label{ex:appropriate}
  \small
  \adjustbox{valign=t}{
    % \setlength\tabcolsep{1.5pt}
    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
      B: &  Well,  I don't have a Mexi-, - & Statement (n/o) \\
      B: & I don't, shouldn't say that, & Self-talk \\
      B: & I don't have an ethnic maid <laughter>. & Statement (n/o) \\

\end{tabulary}}
\end{lingex}

% A[+]: Have, {F uh, } really, - /
% A[t1]: what's the word I'm looking for,  /
% A[sd]: I'm just totally drawing a blank <laughter>. /

% A[\%]: {C And, } {F uh, } cold foo-, {F um, } - /
% A[t1]: what's it called,  /
% A[sd]: I forgot, <laughter>, what it's called, /
% ----

% A[sd]: {D Well, } I don't know T V shows,  /
% A[t1]: what can I tell you, {F um, }  /
% A[sv]: basically junk that's on television <laughter>. -/

% B[sd]: {D Well, } I don't have a Mexi-, - /
% B[t1]: I [ don't, + ] shouldn't say that,  /
% B[sd]: I don't have an ethnic maid <laughter>. /

% Ex. reject
% B[sv]: {C So } I'm old <laughter>. /
% A[ar]: No,  /
% A[sv]: you're not old <laughter>. /

\paragraph{Apology and Downplayer}\label{subs:ap-down}
It is interesting to comment on the parallelisms of laughter usage
in relation to \textit{Apology} and \textit{Downplayer}, represented
in Fig. \ref{fig:orbit} in contrast to \emph{Statement-non-opinion}, in
as much as their graphic representations are more or less mirror-images of each other
 and show how the dialogue acts are 
linked by the pragmatic functions laughter can perform in dialogue.

In both \textit{Apology} and \textit{Downplayer} we observe a rather
higher proportion of occurrences in which the dialogue act is
accompanied by laughter ($\uparrow$) in comparison to other DAs
(Fig. \ref{fig:da-orbits}). In the case of \textit{Apology}, laughter
can be produced to induce benevolence from the partner
\citep{mazzocconiTAC}, while in the case of \textit{Downplayer} the
laughter can be produced to reassure the partner about some situation
that had been appraised as discomforting (classified as \emph{social
incongruity} by \citealp{mazzocconiTAC}) and somehow signal that the
issue should be regarded %\todo{is declined a technical term here? If not I might swap with ``regarded''} 
as not important
\citep{romaniuk2009clinton,gazelaughter}, as in \ref{ex:socInc}.

\begin{lingex}
\item\label{ex:socInc}
  \small
  \adjustbox{valign=t}{
    % \setlength\tabcolsep{1.5pt}
    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
      A: & I don't, I don't think I could do that <laughter>. \# & Statement (n/o) \\
      B: & Oh, it's not bad at all. & Downplayer \\
      A: &  It's, it's a beautiful drive.  & Statement (n/o)\\
\end{tabulary}}
\end{lingex}

The interesting mirror-image %specular\todo{does it work in english? BN: I didn't know this word before but I think so? CH: I have no idea what it means. Can we rephrase so it's understandable to mere mortals??}
patterns
observable in the lower part of the graph can therefore be explained
by considering the relation between the two dialogues acts.  We
observe cases in which an \textit{Apology} is accompanied by a
laughter, and then followed by a \textit{Downplayer}, showing 
that the laughter’s positive effect was attained and successful. This
allows us to explain both the bottom left spike ($\swarrow$) observed for
\textit{Downplayer} (often preceded by an utterance by the
partner containing laughter) and the bottom right spike ($\searrow$) observed
for \emph{Apology} (often followed by an utterance by the
partner containing laughter). In example \ref{ex:apology-downplayer}
both the apology and the downplayer are accompanied by laughter, while
in \ref{ex:sorry} a typical example of a laughter accompanying an \emph{Apology}
is followed by a \emph{Downplayer}.

\begin{lingex}
\item\label{ex:sorry}
  \small
  \adjustbox{valign=t}{
    % \setlength\tabcolsep{1.5pt}
    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
      B: & I'm sorry <laughter>. \# & Apology \\
      A: & That's all right.  / & Downplayer \\
      B: & You,  you were talking about, uh, uh,    & Summarise\\
\end{tabulary}}
\end{lingex}

We now turn to the question of whether our qualitative observations of patters between laughs and dialogue acts can be used to improve a dialogue act recognition task.

% E.g. social inc in general

% B[sd]: [ I don't, + I don't ] think I could do that <laughter>. /
% A[bd]: {F Oh, } it's not bad at all.  /
% A[sd]: [  It's, + it's ] a beautiful drive. /

% A[sd]: I hope you can understand what I s-, \# <laughter>. \# -/
% B[bd]: \# That's okay <laughter>. \#  /
% B[sd]: I got the dryer going --

% E.g. pair apology downplayer
% B[fa]: I'm sorry <laughter>. /
% A[bd]: That's all right.  /
% A[bf]: [ You, + you ] were talking about, {F uh, } {F uh, } --

% A[fa]: I'm sorry to keep you waiting \# <laughter>. \# /
% B[bd]: \# Okay \# <laughter>. /
% A[sd]: {F Uh, } I was calling from work  /

% A[fa]: I'm sorry <laughter>. /
% B[bd]: That's okay.  /
% B[sd]: I'm Bill from Raleigh. /

% A[fa]: {D Well, } I'm sorry <laughter>. /
% B[bd]: That's okay. /
% A[qy]: {F Uh, } did you ever go to Texins at all  when you were working for T I?  /

% A[fa]: {C And } I'm sorry <laughter>. /
% B[bd]: {F Oh, } no. /
% A[sd]: We're just not real big movie goers. /

%of course these are too many examples, but we can choose! ; )

%  by and bd "sYmpathy" and "Downplayers" of sympathy and compliments
%These are subtypes of BACKWARDS-ATTITUDE which express not just acknoweldge or understanding, but also further emotional involvement.

% by   A.44 utt1:  I'm real sorry. /
% Actual apologies (for doing something), as opposed to markers of sympathies, are tagged as "fa", see above.

% bd is any downplayer that speakers use to respond to apologize.

% bd   B.45 utt1:  That's all right. /
% Downplayers are also used to respond to compliments.

%
% \paragraph{action-directive}
% \paragraph{summarise/reformulate }

% \paragraph{agree/accept, appreciation}

% \end{itemize}

% \begin{table}[htbp]
%       \small
%   \centering
%   \begin{tabularx}{\linewidth}{llL}
%     \toprule
%     Speaker & DA & Utterance \\ \midrule
%     A	&Apology	& I'm sorry to keep you waiting \#\texttt{<laughter>}.\#  \\
%     B &Downplayer & \#Okay\# \texttt{<laughter>}. \\
%     A	&sd	& Uh, I was calling from work  \\
%     \bottomrule
%   \end{tabularx}
%   \caption{Example from the SWDA corpus (TODO:SW???). Dialogue acts:
%     \emph{sd}---Statement-non-opinion. Overlapping material is marked
%     with hash signs. }
%   \label{tab:ex:apology-downplayer}
% \end{table}

% \item Agree/accept + Appreciation

\section{The importance of laughter in artificial dialogue act recognition}
\label{sec:dar}

@@

\subsection{Data}\label{sec:data}
We perform experiments on the Switchboard Dialogue Act Corpus (SWDA,
42 dialogue act tags), which is a subset of the larger Switchboard
corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus
(AMI-DA).  AMI uses a smaller tagset of 16 dialogue acts
\citep{GuidelinesDialogueAct2005}.

@@

\begin{table}[ht]
\small
\centering
\begin{tabular}{@{}ll@{}}
\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\\hline
Dyadic                     & Multi-party                             \\
Casual conversation        & Mock business meeting                   \\
Telephone                  & In-person \& video                      \\
English                    & English                                 \\ 
Native speakers            & Native \& non-native speakers           \\ 
%  early '90s                 & 2000s                                   \\
2200 conversations         & 171 meetings                            \\
  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
400k utterances             & 118k utterances                         \\
  3M tokens                  & 1.2M tokens                             \\
\end{tabular}  
\caption{Comparison between Switchboard and the AMI Meeting Corpus
  \label{table:corpora}}
\end{table}

\paragraph{Preprocessing}

We make an effort to normalise transcription conventions across SWDA and AMI.
We remove disfluency annotations and slashes from the end of utterances in SWDA.
In both corpora, acronyms are tokenised as individual letters. 
All utterances are lower-cased.

Utterances are tokenised using a word piece tokeniser \citep{Wu2016} with a vocabulary of 30,000.
We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
We also  prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.

\subsection{The model}
\label{sec:model}
To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorises utterances, and a sequence model that predicts dialogue act tags from the vectorised utterances (Figure~\ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN. It can be explained by the absence of longer distance dependencies on this level of our model.} 
The RNN takes the encoded utterance as input at each time step,
and its hidden state is passed to a simple linear classification layer over dialogue act tags.
Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.

@@

As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
The model uses 100-dimensional word embeddings, which are initialised with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.

@@

\subsection{Experiment 2: laughter and pre-training}
\label{sec:exper-2:-laught}
